Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2015-06-23 text/supp.tex
Revert some thesis-specific modifications
Switch to local .bib files
Add draft section to SOM on skew t

@@

% \renewcommand{\baselinestretch}{\tighttextstretch}
% \normalsize
% \bibliographystyle{apalike}
% \bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}
% \renewcommand{\baselinestretch}{\textstretch}
% \normalsize
%
% ------------------------------
% Supplemental Tables
% ------------------------------

@@

\begin{scriptsize}
%\renewcommand{\baselinestretch}{1.11}
\noindent
{\tt
\input{../analysis/mainids}
}
%\renewcommand{\baselinestretch}{\textstretch}
\end{scriptsize}
\normalsize
%\end{spacing}

>>>>

\subsection{The skewed Student's t distribution}

We fit Gompertz models with skewed Student's t distributed process noise based
on the probability density for the skewed t distribution described in
\citet{fernandez1998}. Their definition equates to the following probability density as implemented in \citet{king2012}:

\[
  \mathrm{Skewed\,Student\mhyphen t}(x) =
\begin{dcases}
\frac{2}{(\gamma + 1/\gamma)}
         \mathrm{Student\mhyphen t}(x \cdot \gamma, \mu \cdot \gamma, \nu, \sigma),& \text{for } x < 0\\
       \frac{2}{(\gamma + 1/\gamma)}
         \mathrm{Student\mhyphen t}(x / \gamma, \mu / \gamma, \nu, \sigma),& \text{for } x \ge 0
\end{dcases}
\]

\smallskip
\noindent
Where $\gamma$ represents the skewness parameter. The distribution is
symmetrical if $\gamma = 1$, left skewed (skewed downwards in abundance) if
$0 < \gamma < 1$, and right skewed (skewed upwards in abundance) if $1 <
\gamma < \infty$. This translates to the log probability:

\[
\mathrm{Skewed\,Student\mhyphen t}(x) =
\begin{dcases}
  \log (2 \gamma) - \log(\gamma^2 + 1) +
  \log \mathrm{Student\mhyphen t}(x \cdot \gamma, \mu \cdot \gamma, \nu, \sigma),& \text{for } x < 0\\
  \log (2 \gamma) - \log(\gamma^2 + 1) +
  \log \mathrm{Student\mhyphen t}(x / \gamma, \mu / \gamma, \nu, \sigma),& \text{for } x \ge 0
\end{dcases}
\]

\smallskip
\noindent
Since Stan only needs the probability density up to an additive constant, we
can replace $\log(2 \gamma)$ in the above for $\log(\gamma)$. The final log
probability density for the skewed Student's t distribution implemented in
Stan\footnote{See the Stan users mailing list: \url{https://groups.google.com/d/msg/stan-users/jeZQnQRUsDs/BeqhicWm1GEJ}} looks like the following:

\begin{verbatim}
real skew_student_t_log(real y, real nu, real mu, real sigma, real skew) {
  real lp;
  lp <- log(skew) - log1p(square(skew));
  if (y < mu)
    return lp + student_t_log(y * skew, nu, mu * skew, sigma);
  else
    return lp + student_t_log(y / skew, nu, mu / skew, sigma);
}
\end{verbatim}

% \[
%   \log p(x) =
% \begin{dcases}
%   \log(2 \gamma) - log(\gamma^2 + 1) +
%     \log \mathrm{dt}(x \gamma, \nu) ,& \text{for } x < 0\\
%   \log(2 \gamma) - log(\gamma^2 + 1) +
%     \log \mathrm{dt}(x / \gamma, \nu) ,& \text{for } x \ge 0
% \end{dcases}
% \]

@@

\bibliographystyle{apalike}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,supp}
%
% ------------------------------
% Supplemental Tables
% ------------------------------

@@

\begin{footnotesize}
%\renewcommand{\baselinestretch}{1.11}
\noindent
{\tt
\input{../analysis/mainids}
}
%\renewcommand{\baselinestretch}{\textstretch}
\end{footnotesize}
\normalsize
%\end{spacing}
